\documentclass{beamer}
\usetheme[titlepagelogo=logopolito,% Logo for the first page
						language=english
                        ]{TorinoTh}
                        
\usepackage[beamer,customcolors]{hf-tikz}
\hfsetfillcolor{alerted text.fg!10}
\hfsetbordercolor{alerted text.fg}

\author{Claudio Fiandrino}
\rel{Mario Rossi}
\title{Beamer2Thesis 2.2, thesis theme for Beamer}
\ateneo{Politecnico di Torino}
\date{\today}

\begin{document}
\input{content_initial.tex}

\begin{frame}[t,fragile]{Configuration}
\begin{itemize}
\item The configuration of the standard theme is:
\begin{itemize}
\item \verb!language=english!
\item \verb!coding=utf8x!
\item \verb!titlepagelogo=name-of-the-logo!
\item \verb!bullet=circle!
\item \verb!pageofpages=of!
\item \verb!titleline=true!
\item \verb!color=blue!
\item \verb!secondcandidate=false!
\item \verb!secondlogo=false!
\end{itemize}
\item Most of them, actually everyone except the \highlight{titlepagelogo}, can be omitted if there are no modifications
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Behavior of alerts}
Each color theme requires different colors to highlight words. To insert alerts by using the \emph{itemize} environment, you can exploit:
\begin{verbatim}
\begin{itemize}
\item<+-| alert@+> Apple
\item<+-| alert@+> Peach
\end{itemize}
\end{verbatim}
For example:
\begin{itemize}
\item<+-| alert@+> Apple
\item<+-| alert@+> Peach
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Another way to highlight words}
If you want to highlight your text out of the enviroment \emph{itemize}, Beamer2Thesis offers you the following possibilities:
\begin{itemize}
\item the standard command \verb!\alert{text}!: it simply highlights your \alert{text}
\item the command \verb!\highlight{text}!: it highlights your \highlight{text} setting it in italic
\item the command \verb!\highlightbf{text}!: it highlights your \highlightbf{text} setting it in bold
\end{itemize}
Of course, the color used, is set accordingly to your choice in the configuration phase.
\end{frame}

\begin{frame}[fragile]{Highlighting formulas}
\begin{itemize}
\item The package \href{http://www.ctan.org/pkg/hf-tikz}{hf-tikz} allows to highlight formulas and formula parts in Beamer with overlay specifications 
\item The adaptation of colors to the theme could be done in this way:
\begin{verbatim}
\usepackage[beamer,customcolors]{hf-tikz}
\hfsetfillcolor{alerted text.fg!10}
\hfsetbordercolor{alerted text.fg}
\end{verbatim}
\item \highlight{Two compilation runs} are required to get the right result!
\item Read the package documentation to find more options; an example will be provided in the next frame.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Highlighting formulas (II)}
\begin{itemize}
\item Example:
\[\tikzmarkin<2->{a}x+\tikzmarkin<1>{b}y\tikzmarkend{b}=10\tikzmarkend{a}\]
\item<2-> Code:
\begin{verbatim}
\[\tikzmarkin<2->{a}x+
  \tikzmarkin<1>{b}y\tikzmarkend{b}
  =10\tikzmarkend{a}\]
\end{verbatim}
\end{itemize}
\end{frame}

\input{content_end}
\end{document}
